SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-09-11 scipy-1.0/paper.tex
Outline background section

\subsection*{History}

@@

>>>>

\section*{Background}

Python ... late 1980s

An matrix / n-dimensional array object ...
matrix.py, numeric, numarray, numpy

Paul Dubois

Travis O

Pearu

-
Gary Strangman

%https://mail.python.org/pipermail/scipy-dev/2001-November/000088.html
%

Eric and Travis V

\subsection*{SciPy Begins}

-  Jun 10, 2001
Travis N. Vaught announced scipy-dev mailing list

- Aug 20, 2001
Eric Jones announced

IPython 2001 first release

Matplotlib 2003 first release

\begin{figure}
\begin{verbatim}
SciPy is an open source package that builds on the strengths of Python and
Numeric providing a wide range of fast scientific and numeric functionality.
SciPy's current module set includes the following:

    Special Functions (Bessel, hanker, Airy, etc.)
    Signal/Image Processing
    2D Plotting capabilities
    Integration
    ODE solvers
    Optimization (simplex, BFGS, Netwon-CG, etc.)
    Genetic Algorithms
    Numeric -> C++ expression compiler
    Parallel programming tools
    Splines and Interpolation
    And other stuff.
\end{verbatim}
\caption{Excerpt from first release announcement.}
\end{figure}

\subsection*{Conferences}

%https://mail.python.org/pipermail/scipy-dev/2002-June/001007.html

SciPy

US, India, Europe

SIAM CSE

PyData

everywhere...

\cite{siamcse09}

%https://archive.siam.org/news/news.php?id=1595

\subsection*{Publications}
CiSE 2007 special issue

CiSE 2011 special issue

@@

\subsection*{SciKits}

% stefan, gael, david, jarrod,

website http://scikits.appspot.com/

statsmodels

scikit-image

scikit-learn
\subsection*{Release History}

ANN: SciPy 0.10 -- Scientific Computing with Python
